The problem and promise of scale in multilayer networks

### 2020-01-23 paper/manuscript.Rmd
network metrics

where x is the number of fixes where individuals A and B were within a given distance of each other, y<sub>A</sub> is the number of fixes from individual A when individual B did not have a simultaneous fix, y<sub>B</sub> is the number of fixes from individual B when individual A did not have a simultaneous fix, and y<sub>AB</sub> is the number of simultaneous fixes from individuals A and B that were separated by more than the given distance (Farine & Whitehead 2015). Social groups were designated if two or more individuals occurred within a given distance of one another at any given time point. For each multilayer network, we calculated XXX metrics (see below).

#### Altering spatial scale

To assess the influence of landcover scale on multilayer networks, we re-sampled our landcover classification map at varying scales. Specifically, we selected scales relevant to caribou ecology. We re-sampled landcover using the **`grainchanger` package/function[???]** (REF) at five scales: 100m, 250m, 500m, 1000m, 2500m. Sampling at 100 and 250m represents fine-scale decision making for caribou during foraging (REF), while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al. 2017). Resampling occurred based on a modal moving window method, where XXXXX. [ALEC YOU'RE GOING TO HAVE TO ADD DETAIL HERE]

**Each modal landcover, and the original are sampled and separate network layers constructed for each. [QW: NOT SURE WHAT THIS MEANS]**

#### Altering the number of observations

### Network metrics

We used Muxviz blah blag whatever to generate XX number of multilayer network metrics. These include four neighborhood-based metrics: degree centrality, multidegree, degree deviation, and neighbours as well as two multilayer [need better term here?] metrics: connective redundancy and relevance (see Glossary for definitions). GOING TO NEED MORE HERE (SEE SMITH-AGUILAR ET AL 2019 PAPER FOR REFERENCE)

@@

>>>>

where x is the number of fixes where individuals A and B were within a given distance of each other, y<sub>A</sub> is the number of fixes from individual A when individual B did not have a simultaneous fix, y<sub>B</sub> is the number of fixes from individual B when individual A did not have a simultaneous fix, and y<sub>AB</sub> is the number of simultaneous fixes from individuals A and B that were separated by more than the given distance (Farine & Whitehead 2015). Social groups were designated if two or more individuals occurred within a given distance of one another at any given time point.

For each multilayer network, we calculated XXX metrics.These included four neighborhood-based metrics: degree centrality, multidegree, degree deviation, and neighbours as well as two multilayer [need better term here?] metrics: connective redundancy and relevance (see Glossary for definitions). GOING TO NEED MORE HERE (SEE SMITH-AGUILAR ET AL 2019 PAPER FOR REFERENCE ON EXPLAINING THESE).

@@

### Scale in multilayer networks

#### Temporal scale

#### Spatial scale

To assess the influence of landcover scale on multilayer networks, we re-sampled our landcover classification map at varying scales. Specifically, we selected scales relevant to caribou ecology. We re-sampled landcover using the `grainchanger` **package/function[???]** (REF) at **five** scales: 100m, 250m, 500m, 1000m, 2500m. Sampling at 100 and 250m represents fine-scale decision making for caribou during foraging (REF), while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al. 2017). Resampling occurred based on a modal moving window method, where **XXXXX. [ALEC YOU'RE GOING TO HAVE TO ADD DETAIL HERE]**

Each modal landcover, and the original are sampled and separate network layers constructed for each. **[QW: NOT SURE WHAT THIS MEANS]**

#### Altering observational scale
